Online Verification of Commutativity

### 2020-10-13 acmPaper/paper.tex
period after captions, added verification as relevent topic

\begin{CCSXML}
    <ccs2012>
       <concept>
           <concept_id>10003752.10003809.10003635.10010038</concept_id>
           <concept_desc>Theory of computation~Dynamic graph algorithms</concept_desc>
           <concept_significance>500</concept_significance>
           </concept>
     </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Theory of computation~Dynamic graph algorithms}

@@

    \begin{subfigure}{0.4\textwidth}
        \begin{tikzpicture}[scale=0.2]
            \tikzstyle{every node}+=[inner sep=0pt]
            \draw [black] (32.8,-8.8) circle (3);
            \draw (32.8,-8.8) node {$meters$};
            \draw [black] (21.5,-21.4) circle (3);
            \draw (21.5,-21.4) node {$feet$};
            \draw [black] (43.7,-21.4) circle (3);
            \draw (43.7,-21.4) node {$miles$};
            \draw [black] (32.4,-33.6) circle (3);
            \draw (32.4,-33.6) node {$wugs$};
            \draw [black] (30.8,-11.03) -- (23.5,-19.17);
            \fill [black] (23.5,-19.17) -- (24.41,-18.9) -- (23.66,-18.24);
            \draw (26.61,-13.64) node [left] {$\times 3.28$};
            \draw [black] (34.76,-11.07) -- (41.74,-19.13);
            \fill [black] (41.74,-19.13) -- (41.59,-18.2) -- (40.84,-18.85);
            \draw (43.7,-13) node [left] {$\times 6.21 \times 10^{-4}$};
            \draw [black] (23.5,-23.64) -- (30.4,-31.36);
            \fill [black] (30.4,-31.36) -- (30.24,-30.43) -- (29.5,-31.1);
            \draw (26.41,-28.96) node [left] {$\times 10$};
            \draw [black] (41.66,-23.6) -- (34.44,-31.4);
            \fill [black] (34.44,-31.4) -- (35.35,-31.15) -- (34.62,-30.47);
            \draw (37.52,-26.04) node [left] {$\times 10^4$};
            \draw [dashed] (29.441,-34.049) arc (-88.02206:-273.82603:12.915);
            \fill [black] (29.44,-34.05) -- (28.62,-33.58) -- (28.66,-34.58);
            \draw (15.56,-20.93) node [left] {$\times 32.8$};
            \draw [dashed] (35.77,-8.425) arc (90.49177:-92.33986:12.828);
            \fill [black] (35.36,-34.07) -- (36.13,-34.6) -- (36.18,-33.6);
            \draw (49.23,-21.46) node [right] {$\times 6.21$};
            \end{tikzpicture}
        \caption{Diagram for the type conversions in the program}
    \end{subfigure}
    \vspace{-2ex}
    \caption{In this sample program, the user implicitly defines two ways to cast variable a from meters to the new unit wugs.
    The definitions are different, and a compiler performing implicit conversion would not know which to choose.}
    \label{fig:typeExample}
\end{figure}

@@

\caption{Finding a spanning set of path pairs, as in section ~\ref{sec:batchBaseline}}\label{algo_spanning_set}
\end{algorithm}

@@

\caption{Finding a minimal spanning set, as described in section ~\ref{sec:batchBaseline}}\label{algo_minimal_spanning_set}
\end{algorithm}

@@

parallelPairs $\gets$ \{\}\;
\For{src in existingGraph.Nodes}{
    \For{snk in existingGraph}{
        \try{}{
            Path pathWithNewEdge $\gets$ FindPath(
                % graph: existingGraph, 
                sourceNode: src,
                sinkNode: newEdge.Source +\;
            newEdge as Path +\;
            FindPath(
                % graph: exisingGraph, 
                sourceNode: newEdge.Sink, 
                sinkNode: snk)\;
            \If{src == snk}{
                pathInOldGraph $\gets$ identity(src)\;
            }
            \Else(){
                Path pathInOldGraph $\gets$ FindPath(
                    % graph: existingGraph, 
                    sourceNode: src, 
                    sinkNode: snk)\;
            }
            parallelPairs.add((pathInOldGraph, pathWithNewEdge))\;
        }
        \catch{PathFindingFailedException}{
           \tcc{No comparable pairs from node src to node snk that need to be checked}
           continue\;
        }
    }
}
\KwRet{parallelPairs}\;
\caption{Online polynomial time algorithm to find parallel pair set}
\label{algo_online_polynomial}
\end{algorithm}

@@

verificationSet $\gets$ \{\}\;
\While{terminalPairGraph.nodes not empty}{
    currentNode $\gets$ terminalPairGraph.node\;
    \tcp*{an arbitrarily chosen node of terminalPairGraph}
    \While{currentNode has predecessors}{
        currentNode $\gets$ predecessor\;
        \tcp*{an arbitrarily chosen predecessor of current Node}
    }
    verificationSet.add(currentNode)\;
    terminalPairGraph.removeAllSuccessors(currentNode)\;
}
\KwRet{verificationSet}\;
\caption{Minimal set finding algorithm}
\label{algo_online_minimal}
\end{algorithm}

@@

\begin{figure}
    % TODO format nicely.
    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_OptimalSet.pdf}
      \caption{~\ref{algo_online_minimal}}
      \label{fig:sfigOptimalTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_Polynomial.pdf}
      \caption{~\ref{algo_online_polynomial}}
      \label{fig:sfigPolynomialTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_NaiveChecker.pdf}
      \caption{Naive baseline}
      \label{fig:sfigNa\"{i}veTvsS}
    \end{subfigure}

@@

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_TwoFlipPathChecker.pdf}
      \caption{Two flip tolerant baseline}
      \label{fig:sfigTwoFlipTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_BatchChecker.pdf}
      \caption{Batch algorithm baseline}
      \label{fig:sfigBatchTvsS}
    \end{subfigure}
    \caption{Plots of scaling of time with input size and density}
    \label{fig:timeVsSize}
\end{figure}

@@

\begin{figure}
    % TODO format nicely.
    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{variance_10_OptimalSet.pdf}
      \caption{~\ref{algo_online_minimal}}
      \label{fig:sfigOptimalSpread}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{variance_10_Polynomial.pdf}
      \caption{~\ref{algo_online_polynomial}}
      \label{fig:sfigPolynomialSpread}
    \end{subfigure}

@@

    \caption{Plots of spread of results}
    \label{fig:variance}
\end{figure}

@@

\begin{table}
    \caption{Output size for 9 node graph of density 0.4, averaged over ten runs}
\begin{tabular}{|c|c|}
    \hline
    Algorithm & average number of output pairs \\
    \hline
    Na\"{i}ve baseline & 39754.9 \\
    Two Flip tolerant & 748.9 \\
    Batch algorithm & 23 \\
    ~\ref{algo_online_polynomial} & 78.3 \\
    ~\ref{algo_online_minimal} & 1 \\
    \hline
\end{tabular}
\label{tab:sizes}
\end{table}

>>>>

\begin{CCSXML}
    <ccs2012>
       <concept>
           <concept_id>10003752.10003809.10003635.10010038</concept_id>
           <concept_desc>Theory of computation~Dynamic graph algorithms</concept_desc>
           <concept_significance>500</concept_significance>
           </concept>
           <concept>
           <concept_id>10003752.10010124.10010138.10010142</concept_id>
           <concept_desc>Theory of computation~Program verification</concept_desc>
           <concept_significance>500</concept_significance>
           </concept>
     </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Theory of computation~Dynamic graph algorithms}
\ccsdesc[500]{Theory of computation~Program verification}

@@

    \begin{subfigure}{0.4\textwidth}
        \begin{tikzpicture}[scale=0.2]
            \tikzstyle{every node}+=[inner sep=0pt]
            \draw [black] (32.8,-8.8) circle (3);
            \draw (32.8,-8.8) node {$meters$};
            \draw [black] (21.5,-21.4) circle (3);
            \draw (21.5,-21.4) node {$feet$};
            \draw [black] (43.7,-21.4) circle (3);
            \draw (43.7,-21.4) node {$miles$};
            \draw [black] (32.4,-33.6) circle (3);
            \draw (32.4,-33.6) node {$wugs$};
            \draw [black] (30.8,-11.03) -- (23.5,-19.17);
            \fill [black] (23.5,-19.17) -- (24.41,-18.9) -- (23.66,-18.24);
            \draw (26.61,-13.64) node [left] {$\times 3.28$};
            \draw [black] (34.76,-11.07) -- (41.74,-19.13);
            \fill [black] (41.74,-19.13) -- (41.59,-18.2) -- (40.84,-18.85);
            \draw (43.7,-13) node [left] {$\times 6.21 \times 10^{-4}$};
            \draw [black] (23.5,-23.64) -- (30.4,-31.36);
            \fill [black] (30.4,-31.36) -- (30.24,-30.43) -- (29.5,-31.1);
            \draw (26.41,-28.96) node [left] {$\times 10$};
            \draw [black] (41.66,-23.6) -- (34.44,-31.4);
            \fill [black] (34.44,-31.4) -- (35.35,-31.15) -- (34.62,-30.47);
            \draw (37.52,-26.04) node [left] {$\times 10^4$};
            \draw [dashed] (29.441,-34.049) arc (-88.02206:-273.82603:12.915);
            \fill [black] (29.44,-34.05) -- (28.62,-33.58) -- (28.66,-34.58);
            \draw (15.56,-20.93) node [left] {$\times 32.8$};
            \draw [dashed] (35.77,-8.425) arc (90.49177:-92.33986:12.828);
            \fill [black] (35.36,-34.07) -- (36.13,-34.6) -- (36.18,-33.6);
            \draw (49.23,-21.46) node [right] {$\times 6.21$};
            \end{tikzpicture}
        \caption{Diagram for the type conversions in the program.}
    \end{subfigure}
    \vspace{-2ex}
    \caption{In this sample program, the user implicitly defines two ways to cast variable a from meters to the new unit wugs.
    The definitions are different, and a compiler performing implicit conversion would not know which to choose.}
    \label{fig:typeExample}
\end{figure}

@@

\caption{Finding a spanning set of path pairs, as in section ~\ref{sec:batchBaseline}.}\label{algo_spanning_set}
\end{algorithm}

@@

\caption{Finding a minimal spanning set, as described in section ~\ref{sec:batchBaseline}.}\label{algo_minimal_spanning_set}
\end{algorithm}

@@

parallelPairs $\gets$ \{\}\;
\For{src in existingGraph.Nodes}{
    \For{snk in existingGraph}{
        \try{}{
            Path pathWithNewEdge $\gets$ FindPath(
                % graph: existingGraph, 
                sourceNode: src,
                sinkNode: newEdge.Source +\;
            newEdge as Path +\;
            FindPath(
                % graph: exisingGraph, 
                sourceNode: newEdge.Sink, 
                sinkNode: snk)\;
            \If{src == snk}{
                pathInOldGraph $\gets$ identity(src)\;
            }
            \Else(){
                Path pathInOldGraph $\gets$ FindPath(
                    % graph: existingGraph, 
                    sourceNode: src, 
                    sinkNode: snk)\;
            }
            parallelPairs.add((pathInOldGraph, pathWithNewEdge))\;
        }
        \catch{PathFindingFailedException}{
           \tcc{No comparable pairs from node src to node snk that need to be checked}
           continue\;
        }
    }
}
\KwRet{parallelPairs}\;
\caption{Online polynomial time algorithm to find parallel pair set.}
\label{algo_online_polynomial}
\end{algorithm}

@@

verificationSet $\gets$ \{\}\;
\While{terminalPairGraph.nodes not empty}{
    currentNode $\gets$ terminalPairGraph.node\;
    \tcp*{an arbitrarily chosen node of terminalPairGraph}
    \While{currentNode has predecessors}{
        currentNode $\gets$ predecessor\;
        \tcp*{an arbitrarily chosen predecessor of current Node}
    }
    verificationSet.add(currentNode)\;
    terminalPairGraph.removeAllSuccessors(currentNode)\;
}
\KwRet{verificationSet}\;
\caption{Minimal set finding algorithm.}
\label{algo_online_minimal}
\end{algorithm}

@@

\begin{figure}
    % TODO format nicely.
    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_OptimalSet.pdf}
      \caption{~\ref{algo_online_minimal}.}
      \label{fig:sfigOptimalTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_Polynomial.pdf}
      \caption{~\ref{algo_online_polynomial}.}
      \label{fig:sfigPolynomialTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_NaiveChecker.pdf}
      \caption{Naive baseline.}
      \label{fig:sfigNa\"{i}veTvsS}
    \end{subfigure}

@@

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_TwoFlipPathChecker.pdf}
      \caption{Two flip tolerant baseline.}
      \label{fig:sfigTwoFlipTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_BatchChecker.pdf}
      \caption{Batch algorithm baseline.}
      \label{fig:sfigBatchTvsS}
    \end{subfigure}
    \caption{Plots of scaling of time with input size and density.}
    \label{fig:timeVsSize}
\end{figure}

@@

\begin{figure}
    % TODO format nicely.
    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{variance_10_OptimalSet.pdf}
      \caption{~\ref{algo_online_minimal}.}
      \label{fig:sfigOptimalSpread}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{variance_10_Polynomial.pdf}
      \caption{~\ref{algo_online_polynomial}.}
      \label{fig:sfigPolynomialSpread}
    \end{subfigure}

@@

    \caption{Plots of spread of results.}
    \label{fig:variance}
\end{figure}

@@

\begin{table}
    \caption{Output size for 9 node graph of density 0.4, averaged over ten runs.}
\begin{tabular}{|c|c|}
    \hline
    Algorithm & average number of output pairs \\
    \hline
    Na\"{i}ve baseline & 39754.9 \\
    Two Flip tolerant & 748.9 \\
    Batch algorithm & 23 \\
    ~\ref{algo_online_polynomial} & 78.3 \\
    ~\ref{algo_online_minimal} & 1 \\
    \hline
\end{tabular}
\label{tab:sizes}
\end{table}
